---
title: "Assignment 1"
author: "German Shepherd Dog"
date: "9/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Our Solution

We chose Washington D.C. as our target region for our analysis. Specifically, we were interested in providing geospatial data for bike tourists. Therefore, we downloaded geojson files for the following: 
  ○ historic monuments
  ○ bikelanes
  ○ tree canopies (so that bikers can take rest after or in-between sightseeing).



## Install packages

We first installed essential packages to plot geospatial data.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
install.packages("tidyverse", quiet = TRUE)
install.packages("sf", quiet = TRUE)
install.packages("spData", quiet = TRUE)
install.packages("ggthemes", quiet = TRUE)
install.packages("ggspatial", quiet = TRUE)
install.packages("Rcpp", quiet = TRUE)
```



## Import libraries

After installing core packages, we must import relevant libraries
to use the functions utilizable in our assignment.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
library(tidyverse, quiet = TRUE)
library(sf, quiet = TRUE)
library(spData, quiet = TRUE)
library(ggthemes, quiet = TRUE)
library(ggspatial, quiet = TRUE)
```



## Loading datasets

As we downloaded geospatial files in geoJSON files, we must read them. 

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
bikelanes <- st_read("Bike Trails.geojson", quiet = TRUE)
landmarks <- st_read("Potential Landmarks.geojson", quiet = TRUE)
canopy <- st_read("Tree Canopy.geojson", quiet = TRUE)
```



## Draw by appropriate layer order and color combinations

As we want to specify the draw order to avoid one layer covering another, we leave ggplot function blank and specify the dataset in geom_sf function. 

Also, we considered removing the gray background and painted it with white.

Last, we erased the longitude and latidue for cleaner look.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() +
geom_sf(data = canopy, aes(color = "Canopies")) +
geom_sf(data = landmarks, aes(fill = "Historic Landmarks"), color = NA) +
geom_sf(data = bikelanes, aes(color = "Bike Lanes")) +
scale_fill_manual(values = "darkgoldenrod1", name = "") +
scale_color_manual(values = c("darkred", "forestgreen"), name = "") +
theme_void()
```



## Default OSM basemap

Oftentimes, the default basemap has the most tidy look.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none") + 
geom_sf(data = landmarks, color = "darkred", fill = "white") +
labs(caption = "Map tiles and data by OpenStreetMap")
```



## Hotstyle

Our team found that the Hotstyle seems pretty useless.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "hotstyle") + 
geom_sf(data = bikelanes, color = "black") +
labs(caption = "Map tiles and data by OpenStreetMap")
```



## HikeBike

HikeBike is useful in showing bikelanes along with those of adjacent cities.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "hikebike") + 
geom_sf(data = bikelanes, color = "darkblue", size = 1) +
labs(caption = "Map tiles and data by OpenStreetMap")
```



## OSM Grayscale

This map has a newspaper look, providing more comfort to the eyes.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "osmgrayscale") + 
geom_sf(data = bikelanes, color = "darkred", size = 1) +
labs(caption = "Map tiles and data by OpenStreetMap")
```



## Stamen black/white

Simpler version of Stamen basemap.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "stamenbw") + 
geom_sf(data = canopy, color = "forestgreen") +
labs(caption = "Map tiles by Stament Design and data by OpenStreetMap")
```



## Stamen watercolor

A picturesque map.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "stamenwatercolor") + 
geom_sf(data = bikelanes, color = "darkred", size = 1) +
labs(caption = "Map tiles by Stament Design and data by OpenStreetMap")
```



## Cartodark

This map is also useless, but at least it looks catchy like a cartoon.

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "cartodark") + 
geom_sf(data = landmarks, color = "goldenrod1", fill = "yellow", size = 1) +
labs(caption = "Map tiles and data by OpenStreetMap")
```



## Cartolight

A pleasant-looking map which has cooler tone than other maps. 

```{r read datasets, message= FALSE, results=hide, warning=FALSE}
ggplot() + 
annotation_map_tile(zoomin = 0, progress = "none", type = "cartolight") + 
geom_sf(data = landmarks, color = "black", fill = "deepskyblue", size = 1) +
labs(caption = "Map tiles and data by OpenStreetMap")
```